\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\tilde{\bm{x}}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\tilde{\bm{x}}_{k}^{i}:=\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\tilde{\bm{x}}_{k}^{i}$, the $i$th (transformed) state sample at the $k$th time step. The schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

@@

For completeness, the proximal algorithm for updating $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ is outlined in Algorithm \ref{algo:KineticProx}. As shown in Fig. \ref{fig:BlockDiagm}, this algorithm takes the pre and post update state samples 
\[\{\tilde{\bm{x}}_{k-1}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k-1}^{i},\bm{\eta}_{k-1}^{i}\right)\}_{i=1}^{N}, \; \{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)\}_{i=1}^{N},\]
and $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}$ as inputs. The Algorithm \ref{algo:KineticProx} has additional

@@

>>>>

\section{Proximal Algorithm}\label{sec:ProxAlgo}
Following \cite{caluya2019TAC}, we solve \eqref{KineticProx} by recursively updating the probability-weighted scattered point clouds $\{\tilde{\bm{x}}_{k}^{i},\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ where 
$$\tilde{\bm{x}}_{k}^{i}:=\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)^{\!\top}, \quad i=1,\hdots,N, \quad k\in\mathbb{N}.$$
Thus, $\tilde{\varrho}_{k}^{i}$ is the joint PDF value obtained from \eqref{KineticProx} at $\tilde{\bm{x}}_{k}^{i}$, the $i$th (transformed) state sample at the $k$th time step. The high level schematic of the algorithm is shown in Fig. \ref{fig:BlockDiagm}.

@@

For completeness, the proximal algorithm for updating $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ is outlined in Algorithm \ref{algo:KineticProx}. As shown in Fig. \ref{fig:BlockDiagm}, this algorithm, at a conceptual level, takes the pre and post update state samples 
\[\{\tilde{\bm{x}}_{k-1}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k-1}^{i},\bm{\eta}_{k-1}^{i}\right)\}_{i=1}^{N}, \; \{\tilde{\bm{x}}_{k}^{i}\}_{i=1}^{N}\equiv\{\left(\bm{\xi}_{k}^{i},\bm{\eta}_{k}^{i}\right)\}_{i=1}^{N},\]
and $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}$ as inputs. The Algorithm \ref{algo:KineticProx} also needs input parameters $h,\varepsilon,N,\delta,L$. Specifically, $h$ is the time-step size, $\varepsilon$ is

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{CompTimeSyntheticPowerSystem.png}
\caption{\small{The computational time for propagating the transient joint PDFs over $\mathbb{T}^{20}\times\mathbb{R}^{20}$ for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\label{fig:CompTimeSynthetic}
\end{figure}
